WIDS 2024 Final Project

### 2024-01-09 Code/R FIle.qmd
state graphs

##### Union employment, CB employment, and full employment (facet by decade)
# should we take the average value per decade?
# add labels for each type of employment
# fix spacing because union employment count is not visible
```{r}
# state and decade
ggplot(full_state_data, aes(x = state_abbreviation)) +
  geom_point(aes(y = employment_count), color = "red") +
  geom_point(aes(y = union_employment_count), color = "blue") +
  geom_point(aes(y = collective_bargain_employment_count), color = "green") +
  facet_wrap(~decade, nrow = 5) +
  labs(x = "State", 
       y = "Number of People Employed")

@@

##### percent union and percent collective bargaining
```{r}

```

>>>>

##### Union employment, CB employment, and full employment (facet by decade)
# should we take the average value per decade?
# add a key for the color of the points
# fix spacing because union employment count is not visible
```{r}
# state and decade
ggplot(full_state_data, aes(x = state_abbreviation)) +
  geom_point(aes(y = employment_count), color = "red") +
  geom_point(aes(y = union_employment_count), color = "blue") +
  geom_point(aes(y = collective_bargain_employment_count), color = "green") +
  facet_wrap(~decade, nrow = 5) +
  labs(x = "State", 
       y = "Number of People Employed")

@@

##### percent union and percent collective bargaining
# should we take the average value per decade?
# add a key for the color of the points
```{r}
# state and decade
ggplot(full_state_data, aes(x = state_abbreviation)) +
  geom_point(aes(y = percent_union), color = "red") +
  geom_point(aes(y = percent_collective_bargain), color = "blue") +
  facet_wrap(~decade, nrow = 5) +
  labs(x = "State", 
       y = "Number of People Employed")

# region and decade
ggplot(full_state_data, aes(x = regions)) +
  geom_point(aes(y = percent_union), color = "red") +
  geom_point(aes(y = percent_collective_bargain), color = "blue") +
  facet_wrap(~decade, nrow = 5) +
  labs(x = "Region", 
       y = "Number of People Employed")
```
